Ideal model selection is impossible

### 2014-11-13 Facticity/Facticity/paper.tex
poep

\newcommand{\M}{\mathcal M}
\newcommand{\K}{\mathcal K}
\newcommand{\X}{\mathcal X}
\newcommand{\C}{\mathcal C}
\newcommand{\B}{\mathbb B}
\newcommand{\D}{\Delta}
\newcommand{\N}{\mathbb N}
\newcommand{\tn}[1]{\textnormal{#1}}
\newcommand{\pair}[1]{\left\langle{#1}\right\rangle}
\newcommand{\concat}{\oplus}
\newcommand{\symb}[1]{\texttt{#1}}

@@

@@

\[
b(i_0)=\min_{i\ge i_0}(L(i)-K(i))
\]

>>>>

\newcommand{\M}{\mathcal M}
\newcommand{\C}{\mathcal C}
\newcommand{\T}{\mathcal T}
\newcommand{\F}{\mathcal F}
\renewcommand{\P}{\mathcal P}
\newcommand{\K}{\mathcal K}
\newcommand{\X}{\mathcal X}
\newcommand{\B}{\mathbb B}
\newcommand{\D}{\Delta}
\newcommand{\N}{\mathbb N}
\newcommand{\tn}[1]{\textnormal{#1}}
\newcommand{\pair}[1]{\left\langle{#1}\right\rangle}
\newcommand{\concat}{\oplus}
\newcommand{\symb}[1]{\texttt{#1}}

@@

\section{Definitions}

\begin{definition}[Models and model classes]
  A \emph{model} is a function $f:\{0,1\}^*\to\{0,1\}^*$. A
  \emph{model class} is a set of models. We distinguish four important
  model classes:
  \begin{itemize}
  \item $\C$ is the set of all partial recursive functions,
  \item $\K\subset\C$ is the set of all partial recursive prefix
    functions,
  \item $\T\subset\C$ is the set of all total recursive functions,
  \item $\P\subset\K$ is the set of all prefix functions such that for
    every infinite binary string the function is defined for a
    prefix. This is the natural analogue of totality in the prefix
  \item $\F\subset\P$ contains, for each finite set $S$, a computable
    surjective function maping the binary sequences of length
    $\lceil\log S\rceil$ onto $S$.
  \end{itemize}
\end{definition}

\begin{definition}[Enumerations]
  Let $\phi_1,\phi_2,\ldots$ be a fixed acceptable enumeration of all partial
  recursive functions, e.g. the enumeration described in \cite{TODO}.  
\end{definition}

\begin{definition}[Representations]
  A pair $(m,y)$ is a \emph{representation} for $x$ if $m$ is a model
  and $m(y)=x$. Given a model class $\M$, define the set of all
  representations for $x$:
  \[
  R^\M(x):=\{(m,y):m\in\M, m(y)=x\}.
  \]
\end{definition}

\begin{definition}[Code length functions]
Define the following code length functions for the representations:
\begin{itemize}
\item $L(m)$ is the length of a self-delimiting description of
  the model $m$, i.e. it is the length function of  a prefix code,
\item $L^m(x)=L(m)+\min\{|y|:m(y)=x\}$ measures the number of bits required to describe both the model $m$ and
  the data $x$ using the model,
\item $L^\M(x)=\min\{L^m(x):m\in\M\}$ measures the number of bits
  required to describe $x$ using the best model in the model class.
\end{itemize}
\end{definition}

\begin{definition}[Candidate set]
  The \emph{candidate models} for $x$ from model class $\M$ are
  \[
  C^\M_c(x):=\{m\in\M:L^m(x)\le L^\M(x)+c\}.
  \]
\end{definition}

\begin{definition}[Sophistication]
  The model complexity, sophistication, or facticity, of a string $x$
  given a model class $\M$ and a constant $c$ is defined by
  \[
  S^\M_c(x):=\min\{L(m):m\in C^\M_c(x)\}.
  \]
\end{definition}

\begin{definition}[Prefix encoding function]
  A prefix encoding function $f:\{0,1\}^*\to\{0,1\}^*$ is an injective
  function that maps the binary strings to a prefix-free set. There
  are prefix encoding functions $g$ with the property that
  $|g(x)|\le|x|+2\log(|x|+2)|$ \cite{TODO}. We fix such a function and
  denote it by $\bar x=g(x)$.
\end{definition}

\paragraph{Kolmogorov's Structure Function}

\begin{itemize}
\item Model class is $\F$
\item Description method for models $L(m)=K(S)$ where $S$ is the range
  of $m$. There is some ambiguity as to the definition of prefix
  complexity for finite sets; discuss and refer to Shen \cite{TODO}.
\end{itemize}

\paragraph{Koppel Sophistication}

\begin{itemize}
\item Model class is $\T$
\item Description method for models is required to be prefix-free, but
  can otherwise be chosen arbitrarily.
\item Koppel uses monotone complexity and discusses infinite strings,
  TODO figure out if and how this affects our results
\end{itemize}

\paragraph{Vit\'anyi's Sophistication / Meaningful Information}

\begin{itemize}
\item Model class is $\T$
\item Description method for models is $L(m)=K(m)$
\item Candidate set is defined differently: $C_c=\{m\in\T:|L^m(x)-K(x)|\le
  c\}$. There appears to be a problem with this definition, because
  the two-part descriptions of $x$ may be shorter than $K(x)$ by
  exploiting the fact that the models do not need to be prefix functions.
\end{itemize}

\paragraph{Antunes's Coarse Sophistication}

\begin{itemize}
\item Model class is $\T$
\item Description method for models is unclear, but appears to be
  taken from Koppel, i.e. arbitrary but self-delimiting.
\item Candidate set is defined differently:
  $C^\T(x)=\{m^*\}$ where $m^*=\argmin_m L(m)+L^m(x)-C(x)$. Thus, there is no slack
  variable and $C^\T$ contains only a single model.
\end{itemize}

\paragraph{Adriaans' Facticity}

\begin{itemize}
\item Model class is $\C$
\item Description method for models is $L(m)=|\bar\imath|$ where
  $\phi_i=m$. The index function is assumed to be \emph{faithful},
  i.e. there is a constant $c$ such that $|i|-C(i)\le c|$ for all $i$.
\item Candidate set is $C^\C_0$.
\item Facticity is actually defined as index length without prefix
  encoding:  $S^\C_0(x):=\min\{|i|:\phi_i\in C^\C_0(x)\}$. But this
  difference is not important for the discussion.
\end{itemize}

@@
